A systematic search for transiting planets using \KT

### 2015-02-05 ms.tex
False positive words

To this end, we (euphamism for look at by eye) each system to identify the
most promising candidates.

\paragraph{False positives}

>>>>

To this end, we (euphamism for look at by eye) each system to identify the
most promising, likely astrophysical signals.

\paragraph{Astrophysical false positives}

A major problem with any transit search is the potential confusion between
transiting planets and eclipsing binaries.
Ground-based surveys before \kepler\ often had a false-positive rate 
of 30-40\%. (because of shit?)
In the primary \kepler\ mission, this number was significantly lower:
the false positive rate was only 5-10\% \citep{morton11}.
Such improvement was enabled by the relatively small pixels, stable 
pointing, and high precision of \kepler.
In \kepler\ data, false positives can be reliably separated from 
planet candidates by looking for differences in the position of the 
centroid of light during transit events with respect to the 
out-of-transit data (e.g. citation), variations in the depth of
alternating transits (e.g. citation), and evidence for ellipsoidal
variations between transits (e.g. citation).

In \KT, we will not be able to rely on any of these techniques to
characterize systems \textit{en masse}. 
There are typically only a handful of transits, meaning differences
between ``odd'' and ``even'' transits must be large to create
a significant difference.
Searching for ellipsoidal varaitions is hindered by the short time
baseline and the increased photometric uncertainty in \KT\ data.
Searching for centroid variations is also more difficult in \KT:
to measure a centroid offset, one must know where the centroid is
supposed to be.
Predicting a centroid position is trivial with \kepler\ data due to the 
remarkably stable pointing of the instrument. 
With \KT\ this is only possible if one understands the pointing of the 
spacecraft at a specific time.
In theory, this is possible: the spacecraft is a rigid body, and by measuring
the mean motion of stars across the detector over time, the 
Euler angles can be inferred at all times.
However, properly measuring positions of stars is a difficult problem:
the centroid depends sensitively on the (unknown) flat field, which must
be simultaneously inferred.
Therefore, false positives caused by background eclipsing binaries which could
be identified as such by \kepler\ data alone will be much more difficult to 
distinguish in \KT\ data, making high-contrast adaptive optics images of 
planet candidates an essential follow-up tool.
